\HeadingItemListStart
	\HeadingItemPlain
		{Projects}{}
	\SubHeadingItem
		{Toric Varieties and Birational Geometry of them (ongoing)}{July 2023 -- Aug. 2023}
		\ItemListStart
			\item Rewriting my MSc thesis.
		\ItemListEnd
	\SubHeadingItem
		{Toric Varieties (MSc Project)}{Nov. 2021 -- Sep. 2022}
		\ItemListStart
			\item Studied the theory of normal toric varieties and wrote a thesis under the supervision of Dr Lai.
			\Item{Topics}
				{\textit{toric monoids}, \textit{affine and projective toric varieties};
				\textit{lattices, cones, fans, and polytopes};
				\textit{classical constructions of toric varieties: product, blow-ups, curves and divisors, resolution of singularities and torus fibration};
				 and \textit{toric surfaces}.}
		\ItemListEnd

	\HeadingItem
		{2023 International Summer School of Algebraic Geometry, Fudan University}{}
		{Algebraic Geometry}{July 2023 -- July 2023}
		\ItemListStart
			\Item{Courses}
				{\textit{Algebraic K-stability theory}, \textit{Moduli space of derived category}, and \textit{P=W conjecture}.}
		\ItemListEnd

	\HeadingItemPlain{Study Group}{}
		\SubHeadingItem{Birational Geometry}{Oct. 2022 -- Apr. 2023}
		\ItemListStart
			\item Attended a weekly reading group supervised by Professor Paolo Cascini at Imperial College London.
			\Item{Topics}
				{\textit{Log pairs} and \textit{boundedness of certain classes of Fano varieties}.}
				% We are reading the paper \href{https://arxiv.org/abs/1603.05765}{\textit{Anti-pluricanonical systems on Fano varieties}} by Professor Caucher Birkar.
		\ItemListEnd
		\SubHeadingItem{Algebraic Topology}{Aug. 2021 -- Sept. 2021}
		\SubHeadingItem{Representation Theory}{May. 2020 -- Jan. 2021}
		\ItemListStart
			\item Co-organized weekly reading groups supervised by Professor Daniel Wong at CUHK(SZ).
			\Item{Topics}
				{\textit{Lie algebras and matrix Lie groups},
				 \textit{classification of semisimple Lie algebras},
				 \textit{Bott periodicity of spheres} and \textit{higher homotopy groups}.}
				% \textit{representations of simple Lie algebras}.}
			% \Item{Textbook(s)}
			% 	{B. C. Hall, \textit{Lie Groups, Lie Algebras and Representations: An Elementary Introduction}}
			% 	% and W. Fulton and J. Harris, \textit{Representation Theory: A first course}
			% 	{A. Hatcher, \textit{Algebraic Topology} and \textit{Vector Bundles and K-Theory}}
		\ItemListEnd

	% \HeadingItem
	% 	{Summer Programme at Girton College, Cambridge}{}
	% 	{Engineering Summer Programme}{July 2019 -- Aug. 2019}
	% 	\ItemListStart
	% 		% \item Attended a one-month summer programme in Girton College, Cambridge.
	% 		\Item{Courses}
	% 			{\textit{Renewable Energy}, \textit{The Jet Engine}, \textit{Nanotechnology}, and \textit{Quantum Technologies}.}
	% 	\ItemListEnd
		
\HeadingItemListEnd

