\HeadingItemListStart
	\HeadingItem
		{Imperial College London}{London, UK}
		{Master of Science (MSc) in Pure Mathematics with \textbf{Distinction} (79.6/100 (A)).}{Oct. 2021 -- Oct. 2022}
		\ItemListStart
			% \Item{Degree}{ . Overall Mark: .}
			\Item{MSc Thesis}{Toric Varieties. Supervisor: Dr Jonathan Lai. Mark: 71.8/100 (A).}
			\Item{Courses}
				{\textit{Algebraic Curves} (A),
				\textit{Manifolds} (A+),
				\textit{Commutative Algebra} (A+),
				\textit{Group Representation Theory} (A+),
				\textit{Algebraic Geometry} (A+),
				\textit{Complex Manifolds} (A),
				\textit{Differential Topology} (A+)
				and \textit{Riemannian Geometry} (A+).}
		\ItemListEnd

	\HeadingItem
		{The Chinese University of Hong Kong, Shenzhen}{Shenzhen, China}
		{Bachelor of Science in Mathematics and Applied Mathematics with Honours, \textbf{First Class}.}{Aug. 2017 -- May 2021}
		\ItemListStart
			% \Item{Degree}{Bachelor of Science with Honours, \textbf{First Class}.}
			\Item{Grade}{GPA 3.5/4, major GPA 3.8/4 (rank 1st).}
			\Item{Selected Courses}
				{\textit{Differential Geometry}, \textit{Introduction to Geometry and Topology}, \textit{Advanced Linear Algebra}, \textit{Abstract Algebra}, \textit{Complex Variables}, \textit{Real Analysis}, \textit{Partial Differential Equations}, \textit{Probability Theory}, \textit{Functional Analysis}.}
			\Item{Awards}
				{AY2019-20/2020-21 Dean's List Award of School of Science and Engineering.}
		\ItemListEnd

	\HeadingItem
		{University of California, Berkeley}{Berkeley, CA, US}
		{Summer Session Visiting Student}{Jun. 2018 -- Aug. 2018}
		\ItemListStart
			\Item{Courses}
				{\textit{Abstract Algebra} and \textit{Research \& Data Analysis}}
		\ItemListEnd

	% \HeadingItem
	% 	{The Affiliated High School to Hangzhou Normal University}{Hangzhou, China}
	% 	{Senior High School}{Sep. 2014 -- May. 2017}
		% Ranked 3670th (out of about 291,300 Zhejiang examinees) in Gaokao.	

\HeadingItemListEnd